Live probes for free

### 2023-07-18 paper/example-programming.tex
Bug fix and demo pics

We initially developed a Java backend using JDI, a debugging interface for Java, to implement the concepts discussed in the previous section. The keep-alive agent includes a method for loading classes into the JVM.

@@

However, it is essential to develop a keep-alive agent specific to each language and to adapt these different methods to the debugging server. These methods depend on both the implementation of the debugging server and the keep-alive agent. Initialization in the DAP protocol is left to the discretion of the debugging server developer, which means that the initialization parameters must be configured for each language.

How the code is loaded also depends on the language. For interpreted languages such as Python, this presents no problem because the code can be interpreted while the agent is running. For Java, classpaths and classes can be added at runtime by redefining the JVM's ClassLoader in the keep-alive agent. For the C language, shared libraries are used to import new code and can be loaded from the agent.

Finally, execution for Java and Python is similar. Unlike the backend, which uses JDI, calling methods directly from the debugger does not trigger breakpoints. To remedy this, execution must be initiated from the agent and not by a debugger command. To this end, the Python and Java agents have fields for referencing a method and its arguments; when this information is entered, the agent launches execution.

\section{Evaluation}
\label{sec:evaluation}
\subsection{Demo : A Small C Live Programming Environment}
\label{sec:demo-small-c}
\subsection{Performance}
\label{sec:performance}

>>>>

We developed a Java backend using JDI, a debugging interface for Java, to implement the concepts discussed in the previous section. 
The keep-alive agent includes a method for loading classes into the JVM.

@@

The implementation for each language includes a keep-alive agent and code to communicate with the debugger and keep-alive agent to provide the interface functionality.
These methods depend on both the implementation of the debugging server and the keep-alive agent. 
The debug server initialisation parameters are specific to each language.

The way in which the code is loaded also depends on the language. 
For interpreted languages such as Python, the code can be interpreted at runtime and then loaded into the debugger's memory. 
For Java, we have extended the ClassLoader to add and modify classpaths and classes at runtime in the keep-alive agent. 
For C, the code is loaded into shared libraries that can be added and reloaded during execution.

Method execution for Java and Python is different to that used in C. 
For Java and Python, calling methods directly from the debugger does not trigger breakpoints for these languages. 
To remedy this, execution must be initiated from the agent and not by a debugger command. 
To do this, the Python and Java agents have fields for referencing a method and its arguments; when this information is entered, the agent starts execution.
For C, as is the case in the backend using JDI, the method call is made from the debugger console.
\section{Evaluation}
\label{sec:evaluation}
\subsection{Demo : A Small C Live Programming Environment}
\label{sec:demo-small-c}
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{img/demo/c.png}
  \caption{Demo of the live programming environment for C.}
  \label{fig:demo}
\end{figure}

\subsection{Performance}
\label{sec:performance}
